Verovio is a fast, portable and lightweight library for engraving \href{http://www.music-encoding.org}{\tt Music Encoding Initiative (M\+EI)} music scores into S\+VG. Verovio can be used as a standalone command-\/line tool for converting a M\+EI files, as the music rendering library for applications, or it can be compiled to Javascript using the Emscripten L\+L\+V\+M-\/to-\/\+Java\+Script compiler.

See the Java\+Script toolkit running in the \href{http://www.verovio.org/mei-viewer.xhtml}{\tt M\+EI Viewer} and check out the \href{http://www.verovio.org/tutorial.xhtml}{\tt tutorial} for its web integration and for enabling user interaction.



Verovio can also render Plain and Easy (P\+AE) code and D\+A\+R\+MS code and has a basic Music\+X\+ML import function. It is designed as a tool usable as a one-\/step conversion tool and it is written in pure standard C++ with no dependencies on third-\/party frameworks and libraries.

Verovio follows the \href{http://www.smufl.org}{\tt Standard Music Font Layout (S\+Mu\+FL)} specification and the font can be changed for personalizing the output.

The project page is \href{http://www.verovio.org}{\tt http\+://www.\+verovio.\+org}. Verovio is available under the L\+G\+PL license (see L\+I\+C\+E\+N\+S\+E.\+txt).

\subsection*{Lib\+M\+EI }

The code for the attribute classes of Verovio are generated from the M\+EI schema using a modified version of Lib\+M\+EI available \href{https://github.com/rism-ch/libmei}{\tt here}. The code generated is included in the Verovio repository and the Lib\+M\+EI repository does not need to be cloned for building Verovio.

\subsection*{Contributing }

If you are willing to contribute to Verovio, please follow the contribution and coding style guidelines.

\subsection*{Example output }

This page was generated with version 0.\+9.\+13-\/dev-\/b953d3b

 